\section*{Methods}

\indent After a charged particle passes through the scintillation detector, the flash of light that is produced is covnerted to a pulse of electrons via the photomulitplier tube. This pulse is then filtered for noise from the detector itself, and amplified by a discriminator/amplifier. After being amplified, the signal is passed into a coincidence circuit that allows us to measure coincidences through a combination of logic modules and delay lines. The condition for the timer to start is that a muon is detected by both of the detectors that are placed on the incoming side of the aluminum slab, and that the detector on the outgoing side of the slab does \textbf{not} detect this muon. 

\indent The condition to stop the timer is that a positron is detected by either of the detectors on the incoming and outgoing sides, but not in both detectors. In order to implement this, a circuit implementing an AND gate, as well as an XOR gate needs to be constructed. It is important to note that we have an exclusive OR gate here, and not a regular OR gate. \textbf{The XOR gate is eliminating events that are necessarily detected by both the detector on the incoming side, and the detector on the outgoing side.}\footnote{This is the answer to the XOR question in the Apparatus section of the muon lab manual.} The set of events for which this is true is characterized by having both a cosmic muon coming from the atmosphere, and also a background muon being detected at the same time. A regular OR gate would have included these events. This is important because we want to isolate detections of muons coming from a single source, namely, the cosmic muons. Using an OR gate would have contaminated our sample with muons that are from the background signal. The rate at which thes events occur is going to be the probability of detecting a positron on BOTH the incoming and outgoing side (B AND C), conditioned on having detected a true cosmic muon (both detectors on the incoming side - given A AND B) . One way to correct for the background noise if we didn't use an XOR gate would be to measure an estimate of the background noise, and subtract off this estimate before performing data analysis. 
